### 2024-06-07 conteudo/background/nlpsimilarity.tex
Add gensim information, 07/06

>>>>

\subsection{Gensim}

Gensim is a open source python library \citep{gensim} which the owners declare themselves as "The fastest library 
for training of vector embeddings - Python or otherwise. The core algorithms in Gensim use battle-hardened, 
highly optimized and parallelized C routines." \citep{gensimsite}. For the velocity of gensim we chose to use this library
for doing our vector embeddings.

In this work we will not explore more alternatives for vector embeddings. We do not want to optimize the computational 
cost or the code clone detection to the state-of-art as they are not the main objectives of our research.
